---
title: "Star Wars Review"
output: html_notebook
---

# Learning Objectives:

- Discuss this class!
- Data Formats
- Learn about notebooks
- What is a data frame?
    - Rows V columns
    - What is a row of data?
    - Data types
- Tour of the RStudio Cloud interface
- How to run a code chunk
- How to render a notebook
- Structure of a R command (function)


# About this class

- This should be a conversation.
- What would you all like to get out of this class?
- Project ideas
- Would you like to:
  - Use your own computers or use Posit Cloud?
  - Would you like to pull the weekly projects or have me send them to you via Canvas?
  - Installation of dependencies!
  - https://epirhandbook.com/en/index.html


# Data Formats:

- [CSV](data/starwars.csv)
- [Excel](data/starwars.xlsx)
- [XML](data/starwars.xml)
  - This is an example of a CCD: https://github.com/HL7/C-CDA-Examples/blob/master/Encounters/Outpatient%20Encounter%20Patient%20Disenrolled/Outpatient%20Encounter%20Patient%20Disenrolled(C-CDA2.1).xml
- [YAML](data/starwars.yaml)


# Setup

```{r}
rm(list = ls())
library(tidyverse)
library(ggrepel)
data(starwars)
```



# Data

```{r}
starwars
```

- What does a single row of data represent?
- What kinds of data types do we have?



# Plotting

## Species

Using a bar plot, figure out which species is the most common in the Star Wars universe.


## Scatter/regression

Draw a scatter plot showing the relationship between mass (x) and height (y).

```{r}

```

OK - We've got ONE REALLY heavy character. Can you filter out the outlier(s) to
get chart we can really read/interpret? 

```{r}

```


And can you add a regression line?

```{r}

```

# Data Management

## Grouping

Can you give me the count of characters from each planet in Star Wars and tell
me which planet has the most characters?

```{r}

```